---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# countValues

<!-- badges: start -->
<!-- badges: end -->

The goal of countValues is to provide an easy way to count occurrences of values in specified columns of a dataset. By grouping data by one or more columns, the function generates a summary count of unique value combinations within those columns.

## Installation

You can install the development version of countValues from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("hedieh-h/countValues")
```

## Example

This is a basic example that demonstrates how to count occurrences within a dataset using the countValues pacakge:

```{r example}
library(countValues)

# Sample data
test_data <- data.frame(
  species_name = c("SERRULATA", "CERASIFERA", "PLATANOIDES", "RUBRUM", NA, "AMERICANA"),
  neighbourhood = c("Downtown", "West End", "Downtown", "Kitsilano", "West End", "Kitsilano"),
  diameter = c(10, 20, 30, 40, NA, 15)
)

# Count occurrences by species and neighbourhood, removing NA values
countValues(test_data, group_by = c("species_name", "neighbourhood"), na.rm = TRUE)
```

